---
title: "Capstone rough"
output: html_document
date: "2026-05-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## import dataset
```{r}
library(readxl)
library(dplyr)
library(mice)
library(stringr)
library(ggplot2)


business_risk_unlabeled_capstone_data_final <- read_excel("business_risk_unlabeled_capstone_data_final.xlsx")
data_final <- business_risk_unlabeled_capstone_data_final#[-1,]

# temp_missing<-data_final[!complete.cases(data_final), ]

```

## Basic data cleaning
```{r}
data_final_all_imp <-subset(data_final, select = -c(client_id, client_reference_hash))

data_final_all_imp$region <- str_to_title(data_final_all_imp$region)
data_final_all_imp$region[data_final_all_imp$region=="gauteng"] <- "Gauteng"
data_final_all_imp$region[data_final_all_imp$region=="Free-State"] <- "Free State"
data_final_all_imp$region[data_final_all_imp$region=="Mpum."] <- "Mpumalanga"
data_final_all_imp$region[data_final_all_imp$region=="Kzn"] <- "Kwazulu-Natal"

data_final_all_imp$sector[is.na(data_final_all_imp$sector)] <- "Other/Missing"

data_final_all_imp$employee_band <- str_to_title(data_final_all_imp$employee_band)
data_final_all_imp$employee_band[data_final_all_imp$employee_band=="Med"] <- "Medium"


data_final_all_imp$acquisition_channel[is.na(data_final_all_imp$acquisition_channel)] <- "Other/Missing"
n_distinct(data_final_all_imp$region)
n_distinct(data_final_all_imp$sector)
n_distinct(data_final_all_imp$employee_band)
n_distinct(data_final_all_imp$acquisition_channel)
```

######Testing if categorical has pattern with missingness #####

# creates indicator variables for the categorical variables. 
# so then the 1 and 0 becomes the Y variables/output that we use to see if the categorical variables
# predict the missingness.
# so 1 if there is missingness in the row of the categorical variable 0 if not
# does this for all missing values and all categorical variables
# see if MAR or maybe MCAR with categorical variables

# CTS done in SAS so need to get that into R still

###### Agree on this so dont need to change ###### 

```{r}


data_test <- data_final_all_imp %>%
  mutate(
    miss_1 = as.numeric(is.na(quick_ratio)),
    miss_2 = as.numeric(is.na(ebit_margin)),
    miss_3 = as.numeric(is.na(employee_growth)),
    miss_4 = as.numeric(is.na(web_traffic_growth))
  )


model_miss_1 <- glm(miss_1 ~ sector + region + primary_product + acquisition_channel+ employee_band + marketing_segment_code, 
                data = data_test, 
                family = binomial)

summary(model_miss_1)
# Lyk my market_segment --> codeD03 is related to if quick_ratio is missing

model_miss_2 <- glm(miss_2 ~ sector + region + primary_product + acquisition_channel+ employee_band + marketing_segment_code, 
                    data = data_test, 
                    family = binomial)

summary(model_miss_2)
# Lyk my market_segment --> codeC91 is related to if ebit_margin is missing


model_miss_3 <- glm(miss_3 ~ sector + region + primary_product + acquisition_channel+ employee_band + marketing_segment_code, 
                    data = data_test, 
                    family = binomial)

summary(model_miss_3)
# lyk ook soos MCAR 

model_miss_4 <- glm(miss_4 ~ sector + region + primary_product + acquisition_channel+ employee_band + marketing_segment_code, 
                    data = data_test, 
                    family = binomial)

summary(model_miss_4)
# lyk my region --> western cape is related to if web_traffic_growth is missing 




# factorise vir die MI
data_final_all_imp$sector <- as.factor(data_final_all_imp$sector)
data_final_all_imp$region <- as.factor(data_final_all_imp$region)
data_final_all_imp$primary_product <- as.factor(data_final_all_imp$primary_product)
data_final_all_imp$acquisition_channel <- as.factor(data_final_all_imp$acquisition_channel)
data_final_all_imp$employee_band <- as.factor(data_final_all_imp$employee_band)
data_final_all_imp$marketing_segment_code <- as.factor(data_final_all_imp$marketing_segment_code)
```

## Using Multiple imputation to fill in the missing values
# creates/generates possible values for each missing value based on the data
# does this m=25 times
# this is a must and we will have to use all m datasets to improve stability and accuracy 

```{r}
imp_all <- mice(data_final_all_imp, m=25, method="pmm", seed=42)
imp_all$loggedEvents
imp_all_data <- imp_all$data
densityplot(imp_all)
all_MI_data_final <- complete(imp_all, "long")
```


##Unsupervised feature selection using FAMD
# Doing FAMD on the entire dataset. 
# Dont split datasets into smaller subgroups 
# My thinking is splitting into subgroups will then ignore/destroy possible 
# interactions/correlations between variables that are in different groups

# FAMD works for both categorical and cts variables
# doing it on entire dataset ensures no interactions/correlations between variables are missed
# FAMD package internally handles this
# Must do on all m datasets 
```{r}
library(FactoMineR)
library(factoextra)

# only a few of the datasets. Should run everything for final answers 
X_1<- complete(imp_all, action=1)
X_2<-complete(imp_all, action=2)
X_5<-complete(imp_all, action=5)
X_10<-complete(imp_all, action=10)
X_20<-complete(imp_all, action=20)
X_25<-complete(imp_all, action=25)

X_3<- complete(imp_all, action=3)
X_4<-complete(imp_all, action=4)
X_6<-complete(imp_all, action=6)
X_7<-complete(imp_all, action=7)
X_8<-complete(imp_all, action=8)
X_9<-complete(imp_all, action=9)

X_11<- complete(imp_all, action=11)
X_12<-complete(imp_all, action=12)
X_13<-complete(imp_all, action=13)
X_14<-complete(imp_all, action=14)
X_15<-complete(imp_all, action=15)
X_16<-complete(imp_all, action=16)

X_17<- complete(imp_all, action=17)
X_18<-complete(imp_all, action=18)
X_19<-complete(imp_all, action=19)
X_21<-complete(imp_all, action=21)
X_22<-complete(imp_all, action=22)
X_23<-complete(imp_all, action=23)

X_24<- complete(imp_all, action=24)

# Run FAMD
res_famd <- FAMD(X_1, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_2 <- FAMD(X_2, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_5 <- FAMD(X_5, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_10 <- FAMD(X_10, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_20 <- FAMD(X_20, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_25 <- FAMD(X_25, 
                 ncp = 35,      
                 graph = FALSE)

res_famd_3 <- FAMD(X_3, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_4 <- FAMD(X_4, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_6 <- FAMD(X_6, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_7 <- FAMD(X_7, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_8 <- FAMD(X_8, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_9 <- FAMD(X_9, 
                    ncp = 35,      
                    graph = FALSE)

res_famd_11 <- FAMD(X_11, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_12 <- FAMD(X_12, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_13 <- FAMD(X_13, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_14 <- FAMD(X_14, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_15 <- FAMD(X_15, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_16 <- FAMD(X_16, 
                    ncp = 35,      
                    graph = FALSE)

res_famd_17 <- FAMD(X_17, 
                 ncp = 35,      
                 graph = FALSE)
res_famd_18 <- FAMD(X_18, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_19 <- FAMD(X_19, 
                   ncp = 35,      
                   graph = FALSE)
res_famd_21 <- FAMD(X_21, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_22 <- FAMD(X_22, 
                    ncp = 35,      
                    graph = FALSE)
res_famd_23 <- FAMD(X_23, 
                    ncp = 35,      
                    graph = FALSE)

res_famd_24 <- FAMD(X_24, 
                 ncp = 35,      
                 graph = FALSE)


res_famd_list <- list(
  res_famd, res_famd_2, res_famd_3, res_famd_4, res_famd_5,
  res_famd_6, res_famd_7, res_famd_8, res_famd_9, res_famd_10,
  res_famd_11, res_famd_12, res_famd_13, res_famd_14, res_famd_15,
  res_famd_16, res_famd_17, res_famd_18, res_famd_19, res_famd_20,
  res_famd_21, res_famd_22, res_famd_23, res_famd_24, res_famd_25
)

eig_matrix <- do.call(rbind, lapply(res_famd_list, function(res) {
  get_eigenvalue(res)[, "variance.percent"]
}))

pooled_var_percent <- colMeans(eig_matrix)
pooled_eig_df <- data.frame(
  dim            = seq_along(pooled_var_percent),
  variance       = pooled_var_percent,
  cumul_variance = cumsum(pooled_var_percent)
)
print(pooled_eig_df[1:35, ])
#Pooled scree plot 
dims_to_keep <- 35  
ggplot(pooled_eig_df[1:35, ], aes(x = dim, y = variance)) +
  geom_col(fill = "steelblue", alpha = 0.7) +
  geom_line(aes(y = variance), colour = "steelblue", linewidth = 0.8) +
  geom_point(aes(y = variance), colour = "steelblue", size = 2) +
  geom_line(aes(y = cumul_variance), colour = "firebrick",
            linewidth = 0.8, linetype = "dashed") +
  geom_point(aes(y = cumul_variance), colour = "firebrick", size = 2) +
  geom_vline(xintercept = dims_to_keep + 0.5,
             linetype = "dotted", linewidth = 0.8, colour = "grey30") +
  geom_hline(yintercept = 70, linetype = "dashed",
             colour = "firebrick", alpha = 0.4) +
  annotate("text", x = dims_to_keep + 0.7, y = max(pooled_var_percent) * 0.95,
           label = paste("Keep:", dims_to_keep, "dims"), hjust = 0, size = 3.5) +
  scale_y_continuous(
    name = "Average % Variance Explained (bars)",
    sec.axis = sec_axis(~ ., name = "Cumulative % Variance (red dashed)")
  ) +
  labs(
    title = "Pooled FAMD Scree Plot (averaged across all imputed datasets)",
    subtitle = "Red dashed = cumulative  |  Horizontal line = 70% threshold",
    x = "Dimension"
  ) +
  theme_minimal(base_size = 13)

X_list <- list(
  X_1, X_2, X_3, X_4, X_5, X_6, X_7, X_8, X_9, X_10,
  X_11, X_12, X_13, X_14, X_15, X_16, X_17, X_18, X_19, X_20,
  X_21, X_22, X_23, X_24, X_25
)

contrib_matrix <- do.call(rbind, lapply(res_famd_list, function(res) {
  rowSums(res$var$contrib[, 1:dims_to_keep, drop = FALSE])
}))
pooled_contribs <- colMeans(contrib_matrix)

selected_vars_list <- lapply(X_list, function(x) {
  threshold <- 100 / ncol(x) * 0.2
  names(pooled_contribs[pooled_contribs > threshold])
})

X_reduced_list <- lapply(seq_along(X_list), function(i) {
  X_list[[i]][, selected_vars_list[[i]], drop = FALSE]
})


cat("Variables kept across all imputations:\n")
print(Reduce(intersect, selected_vars_list))

# 1. Calculate the total contribution across the dimensions you decided to keep
# Based on skree we use the first 35 dimensions (elbow)
# since the variance explained is low we try to include as much as possible
# this indicates that after  dimension the data no longer has a dominant structure 
# 
dims_to_keep <- 1:35
total_contribs <- rowSums(res_famd$var$contrib[, dims_to_keep])
total_contribs_2 <- rowSums(res_famd_2$var$contrib[, dims_to_keep])
total_contribs_5 <- rowSums(res_famd_5$var$contrib[, dims_to_keep])
total_contribs_10 <- rowSums(res_famd_10$var$contrib[, dims_to_keep])
total_contribs_20 <- rowSums(res_famd_20$var$contrib[, dims_to_keep])
total_contribs_25 <- rowSums(res_famd_25$var$contrib[, dims_to_keep])

total_contribs_3 <- rowSums(res_famd_3$var$contrib[, dims_to_keep])
total_contribs_4 <- rowSums(res_famd_4$var$contrib[, dims_to_keep])
total_contribs_6 <- rowSums(res_famd_6$var$contrib[, dims_to_keep])
total_contribs_7 <- rowSums(res_famd_7$var$contrib[, dims_to_keep])
total_contribs_8 <- rowSums(res_famd_8$var$contrib[, dims_to_keep])
total_contribs_9 <- rowSums(res_famd_9$var$contrib[, dims_to_keep])

total_contribs_11 <- rowSums(res_famd_11$var$contrib[, dims_to_keep])
total_contribs_12 <- rowSums(res_famd_12$var$contrib[, dims_to_keep])
total_contribs_13 <- rowSums(res_famd_13$var$contrib[, dims_to_keep])
total_contribs_14 <- rowSums(res_famd_14$var$contrib[, dims_to_keep])
total_contribs_15 <- rowSums(res_famd_15$var$contrib[, dims_to_keep])
total_contribs_16 <- rowSums(res_famd_16$var$contrib[, dims_to_keep])

total_contribs_17 <- rowSums(res_famd_17$var$contrib[, dims_to_keep])
total_contribs_18 <- rowSums(res_famd_18$var$contrib[, dims_to_keep])
total_contribs_19 <- rowSums(res_famd_19$var$contrib[, dims_to_keep])
total_contribs_21 <- rowSums(res_famd_21$var$contrib[, dims_to_keep])
total_contribs_22 <- rowSums(res_famd_22$var$contrib[, dims_to_keep])
total_contribs_23 <- rowSums(res_famd_23$var$contrib[, dims_to_keep])

total_contribs_24 <- rowSums(res_famd_24$var$contrib[, dims_to_keep])


#### deciding varaibles to keep (my approach) #####
# Average contribution = 100 / total number of variables
# keep al variables that contribute atleast 100% of the average contribution for the number of dimension we choose
threshold <- (100 * length(dims_to_keep)) / ncol(X_1) * 0.2# keep al variables that contribute atleast 100% of the average contribution for the number of dimension we choose. basically standardise per dimension
threshold_5 <- (100 * length(dims_to_keep)) / ncol(X_5) * 0.2
threshold_10 <- (100 * length(dims_to_keep))/ ncol(X_10) * 0.2
threshold_20 <- (100 * length(dims_to_keep))/ ncol(X_20) * 0.2
threshold_25 <- (100 * length(dims_to_keep))/ ncol(X_25) * 0.2

threshold_2 <- (100 * length(dims_to_keep))/ ncol(X_2)* 0.2
threshold_3 <- (100 * length(dims_to_keep))/ ncol(X_3)* 0.2
threshold_4 <- (100 * length(dims_to_keep))/ ncol(X_4) * 0.2
threshold_6 <- (100 * length(dims_to_keep))/ ncol(X_6) * 0.2
threshold_7 <- (100 * length(dims_to_keep))/ ncol(X_7)* 0.2

threshold_8 <- (100 * length(dims_to_keep))/ ncol(X_8) * 0.2
threshold_9 <- (100 * length(dims_to_keep))/ ncol(X_9) * 0.2
threshold_11 <- (100 * length(dims_to_keep))/ ncol(X_11) * 0.2
threshold_12 <- (100* length(dims_to_keep))/ ncol(X_12) * 0.2

threshold_13 <- (100 * length(dims_to_keep))/ ncol(X_13) * 0.2
threshold_14 <- (100 * length(dims_to_keep))/ ncol(X_14) * 0.2
threshold_15 <- (100 * length(dims_to_keep))/ ncol(X_15) * 0.2
threshold_16 <- (100 * length(dims_to_keep))/ ncol(X_16) * 0.2

threshold_17 <- (100 * length(dims_to_keep))/ ncol(X_17) * 0.2
threshold_18 <- (100 * length(dims_to_keep))/ ncol(X_18) * 0.2
threshold_19 <- (100 * length(dims_to_keep))/ ncol(X_19) * 0.2
threshold_21 <- (100 * length(dims_to_keep))/ ncol(X_21) * 0.2

threshold_22 <- (100 * length(dims_to_keep))/ ncol(X_22) * 0.2
threshold_23 <- (100 * length(dims_to_keep))/ ncol(X_23) * 0.2
threshold_24 <- (100 * length(dims_to_keep))/ ncol(X_24)* 0.2

# so lots of var provides some contribution towards the variance

selected_vars <- names(total_contribs[total_contribs > threshold])
selected_vars_2 <- names(total_contribs_2[total_contribs_2 > threshold_2])
selected_vars_5 <- names(total_contribs_5[total_contribs_5 > threshold_5])
selected_vars_10 <- names(total_contribs_10[total_contribs_10 > threshold_10])
selected_vars_20 <- names(total_contribs_20[total_contribs_20 > threshold_20])
selected_vars_25 <- names(total_contribs_25[total_contribs_25 > threshold_25])

selected_vars_3 <- names(total_contribs_3[total_contribs_3 > threshold_3])
selected_vars_4 <- names(total_contribs_4[total_contribs_4 > threshold_4])
selected_vars_6 <- names(total_contribs_6[total_contribs_6 > threshold_6])
selected_vars_7 <- names(total_contribs_7[total_contribs_7 > threshold_7])
selected_vars_8 <- names(total_contribs_8[total_contribs_8 > threshold_8])
selected_vars_9 <- names(total_contribs_9[total_contribs_9 > threshold_9])

selected_vars_11 <- names(total_contribs_11[total_contribs_11 > threshold_11])
selected_vars_12 <- names(total_contribs_12[total_contribs_12 > threshold_12])
selected_vars_13 <- names(total_contribs_13[total_contribs_13 > threshold_13])
selected_vars_14 <- names(total_contribs_14[total_contribs_14 > threshold_14])
selected_vars_15 <- names(total_contribs_15[total_contribs_15 > threshold_15])
selected_vars_16 <- names(total_contribs_16[total_contribs_16 > threshold_16])

selected_vars_17 <- names(total_contribs_17[total_contribs_17 > threshold_17])
selected_vars_18 <- names(total_contribs_18[total_contribs_18 > threshold_18])
selected_vars_19 <- names(total_contribs_19[total_contribs_19 > threshold_19])
selected_vars_21 <- names(total_contribs_21[total_contribs_21 > threshold_21])
selected_vars_22 <- names(total_contribs_22[total_contribs_22 > threshold_22])
selected_vars_23 <- names(total_contribs_23[total_contribs_23 > threshold_23])

selected_vars_24 <- names(total_contribs_24[total_contribs_24 > threshold_24])


# 4. Create new, reduced dataset
# removes non-informative results. 
X_1_reduced <- X_1[, selected_vars]
X_2_reduced <- X_2[, selected_vars_2]
X_5_reduced <- X_5[, selected_vars_5]
X_10_reduced <- X_10[, selected_vars_10]
X_20_reduced <- X_20[, selected_vars_20]
X_25_reduced <- X_25[, selected_vars_25]

X_3_reduced <- X_3[, selected_vars_3]
X_4_reduced <- X_4[, selected_vars_4]
X_6_reduced <- X_6[, selected_vars_6]
X_7_reduced <- X_7[, selected_vars_7]
X_8_reduced <- X_8[, selected_vars_8]
X_9_reduced <- X_9[, selected_vars_9]

X_11_reduced <- X_11[, selected_vars_11]
X_12_reduced <- X_12[, selected_vars_12]
X_13_reduced <- X_13[, selected_vars_13]
X_14_reduced <- X_14[, selected_vars_14]
X_15_reduced <- X_15[, selected_vars_15]
X_16_reduced <- X_16[, selected_vars_16]

X_17_reduced <- X_17[, selected_vars_17]
X_18_reduced <- X_18[, selected_vars_18]
X_19_reduced <- X_19[, selected_vars_19]
X_21_reduced <- X_21[, selected_vars_21]
X_22_reduced <- X_22[, selected_vars_22]
X_23_reduced <- X_23[, selected_vars_23]

X_24_reduced <- X_24[, selected_vars_24]
# Run FAMD on the reduced dataset 
# do this to get the FAMD coordinates. this is transformed so that we can work with cts and categorical variables
# this then encodes the data to be used in mclust to help
# also a dimensionality reduction technique
X_1_reduced_res_FAMD  <- FAMD(X_1_reduced,  ncp = 35, graph = FALSE)
X_2_reduced_res_FAMD  <- FAMD(X_2_reduced,  ncp = 35, graph = FALSE)
X_3_reduced_res_FAMD  <- FAMD(X_3_reduced,  ncp = 35, graph = FALSE)
X_4_reduced_res_FAMD  <- FAMD(X_4_reduced,  ncp = 35, graph = FALSE)
X_5_reduced_res_FAMD  <- FAMD(X_5_reduced,  ncp = 35, graph = FALSE)
X_6_reduced_res_FAMD  <- FAMD(X_6_reduced,  ncp = 35, graph = FALSE)
X_7_reduced_res_FAMD  <- FAMD(X_7_reduced,  ncp = 35, graph = FALSE)
X_8_reduced_res_FAMD  <- FAMD(X_8_reduced,  ncp = 35, graph = FALSE)
X_9_reduced_res_FAMD  <- FAMD(X_9_reduced,  ncp = 35, graph = FALSE)
X_10_reduced_res_FAMD <- FAMD(X_10_reduced, ncp = 35, graph = FALSE)
X_11_reduced_res_FAMD <- FAMD(X_11_reduced, ncp = 35, graph = FALSE)
X_12_reduced_res_FAMD <- FAMD(X_12_reduced, ncp = 35, graph = FALSE)
X_13_reduced_res_FAMD <- FAMD(X_13_reduced, ncp = 35, graph = FALSE)
X_14_reduced_res_FAMD <- FAMD(X_14_reduced, ncp = 35, graph = FALSE)
X_15_reduced_res_FAMD <- FAMD(X_15_reduced, ncp = 35, graph = FALSE)
X_16_reduced_res_FAMD <- FAMD(X_16_reduced, ncp = 35, graph = FALSE)
X_17_reduced_res_FAMD <- FAMD(X_17_reduced, ncp = 35, graph = FALSE)
X_18_reduced_res_FAMD <- FAMD(X_18_reduced, ncp = 35, graph = FALSE)
X_19_reduced_res_FAMD <- FAMD(X_19_reduced, ncp = 35, graph = FALSE)
X_20_reduced_res_FAMD <- FAMD(X_20_reduced, ncp = 35, graph = FALSE)
X_21_reduced_res_FAMD <- FAMD(X_21_reduced, ncp = 35, graph = FALSE)
X_22_reduced_res_FAMD <- FAMD(X_22_reduced, ncp = 35, graph = FALSE)
X_23_reduced_res_FAMD <- FAMD(X_23_reduced, ncp = 35, graph = FALSE)
X_24_reduced_res_FAMD <- FAMD(X_24_reduced, ncp = 35, graph = FALSE)
X_25_reduced_res_FAMD <- FAMD(X_25_reduced, ncp = 35, graph = FALSE)

#these are the variables that are kept
print(names(X_1_reduced))
# Check how many you kept
print(paste("Original features:", ncol(X_1)))
print(paste("Selected features:", length(selected_vars)))

# We use the FAMD varaibles to read this into the mclust##
# Extract all 35 the dimensions
famd_dims_final_1  <- X_1_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_2  <- X_2_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_3  <- X_3_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_4  <- X_4_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_5  <- X_5_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_6  <- X_6_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_7  <- X_7_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_8  <- X_8_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_9  <- X_9_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_10 <- X_10_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_11 <- X_11_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_12 <- X_12_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_13 <- X_13_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_14 <- X_14_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_15 <- X_15_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_16 <- X_16_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_17 <- X_17_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_18 <- X_18_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_19 <- X_19_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_20 <- X_20_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_21 <- X_21_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_22 <- X_22_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_23 <- X_23_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_24 <- X_24_reduced_res_FAMD$ind$coord[, 1:35]
famd_dims_final_25 <- X_25_reduced_res_FAMD$ind$coord[, 1:35]

```

## LCA with Mclsut 1: 
#             We use mclust()
#             we run this with possible 2-->6 clusters to be chosen from (1 cluster is                meaningless)
#             we run this with 6 possible models
#             this uses BIC to determine the best model 
#             and best number of clusters
#             internally it runs all combinations of clusters and models
#             defualt is 250 iterations max


# The results showed using majority vote that VVE + 4 clusters gives us the best BIC
# This is then the model and number of clusters we chose
# (explenations of model meanings inside this chunk)
#
# (dont need to run this. this is only to show where i get the info from)
```{r}
library(mclust)


# Determines the size and shape of the models
# For now assume not realistic to assume same size 
# last letter = V = more complex since oriantation of clusters is different for each cluster

# EII=equal size + equal shape + (very low complexity + spherical)
# VII=variable szie + equal shape + (low complexity + spherical)
# EEI=equal size + equal shape + (low complexity + diagonal)

# VEI=variable szie + equal shape + (medium complex + diagonal)
# EVI=equal size + variable shape + (medium complex + diagonal)
# VVI=variable szie + variable shape + (medium complex + diagonal)

# EEE=equal size + equal shape + (high complexity + ellipsoidal)
# EVE=equal size + variable shape + (high complexity + ellipsoidal)
# VEE=variable szie + equal shape + (high complexity + ellipsoidal) 

# VVE=variable szie + variable shape +(very high complexity + ellipsoidal) 
# EEV=equal size + equal shape + (very high complexity + ellipsoidal)
# VEV=equal size + equal shape + (very high complexity + ellipsoidal)

# EVV=equal size + variable shape + (extreme complexity + ellipsoidal)
# VVV=variable szie + variable shape + (extreme complexity + ellipsoidal)


# use 
# c("EII", "VII", "EEI", "VVI", "EEE", "VVV") very short with ok-ish results not great
# c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE") better results but takes long
model_selection <- mclust(X_1_reduced, G = 2:6, 
                          modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

model_selection_2 <- Mclust(X_2_reduced, G = 2:7, 
                          modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

# this option is a good all rounder with variable/equal sizes + variable/equal shapes + ellipsoid/diag/sphereical 


model_selection_5 <- mclust(X_5_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_10 <- Mclust(X_10_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_20 <- Mclust(X_20_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_25 <- Mclust(X_25_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

model_selection_3 <- Mclust(X_3_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_4 <- Mclust(X_4_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_6 <- Mclust(X_6_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_7 <- Mclust(X_7_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_8 <- Mclust(X_8_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_9 <- Mclust(X_9_reduced, G=2:6, 
                            modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

model_selection_11 <- Mclust(X_11_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_12 <- Mclust(X_12_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_13 <- Mclust(X_13_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_14 <- Mclust(X_14_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_15 <- Mclust(X_15_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_16 <- Mclust(X_16_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

model_selection_17 <- Mclust(X_17_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_18 <- Mclust(X_18_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_19 <- Mclust(X_19_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_21 <- Mclust(X_21_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_22 <- Mclust(X_22_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))
model_selection_23 <- Mclust(X_23_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

model_selection_24 <- Mclust(X_24_reduced, G=2:6, 
                             modelNames = c("EII", "VII", "EEI", "VVI", "VEE", "VVV", "VVE"))

mclust_models_list <- list(
  "Imputation_1"  = model_selection,
  "Imputation_2"  = model_selection_2,
  "Imputation_3"  = model_selection_3,
  "Imputation_4"  = model_selection_4,
  "Imputation_5"  = model_selection_5,
  "Imputation_6"  = model_selection_6,
  "Imputation_7"  = model_selection_7,
  "Imputation_8"  = model_selection_8,
  "Imputation_9"  = model_selection_9,
  "Imputation_10" = model_selection_10,
  "Imputation_11" = model_selection_11,
  "Imputation_12" = model_selection_12,
  "Imputation_13" = model_selection_13,
  "Imputation_14" = model_selection_14,
  "Imputation_15" = model_selection_15,
  "Imputation_16" = model_selection_16,
  "Imputation_17" = model_selection_17,
  "Imputation_18" = model_selection_18,
  "Imputation_19" = model_selection_19,
  "Imputation_20" = model_selection_20,
  "Imputation_21" = model_selection_21,
  "Imputation_22" = model_selection_22,
  "Imputation_23" = model_selection_23,
  "Imputation_24" = model_selection_24,
  "Imputation_25" = model_selection_25
)


# Shows that using majority vote that VVV + K=6 clusters is the best
# VVI is second so if really want could use that
# VVI however does tend to say biggest possible k is the best wich is not good
best_choices <- data.frame(
  Dataset    = names(mclust_models_list),
  Best_Model = sapply(mclust_models_list, function(x) x$modelName),
  Best_G     = sapply(mclust_models_list, function(x) x$G),
  Best_BIC = sapply(mclust_models_list, function(x) x$BIC[1]),
  stringsAsFactors = FALSE
)
best_name <- model_selection$modelName
best_k<-model_selection$G

```

## Using majority vote we decide on model=VVE
#                                        Variable shape of clusters
#                                        variable size of clusters
#                                        equal orientation
#                                        (Ellipsoidal)
#                                       num clusters = 4

# we now fit the final models using mclust to determine final clusters of the data
# (again this also takes +-15 minutes each to run )
```{r}
library(mclust)
k<-4
model_selection_final <- Mclust(famd_dims_final_1,G=k,modelNames = "VVE")
model_selection_2_final <- Mclust(famd_dims_final_2,G=k,modelNames = "VVE")
model_selection_5_final <- Mclust(famd_dims_final_5,G=k,modelNames = "VVE")
model_selection_10_final <- Mclust(famd_dims_final_10,G=k,modelNames = "VVE")#lank
model_selection_20_final <- Mclust(famd_dims_final_20,G=k,modelNames = "VVE")
model_selection_25_final <- Mclust(famd_dims_final_25,G=k, modelNames = "VVE")


model_selection_3_final <- Mclust(famd_dims_final_3,G=k,modelNames = "VVE")
model_selection_4_final <- Mclust(famd_dims_final_4,G=k,modelNames = "VVE")
model_selection_6_final <- Mclust(famd_dims_final_6,G=k,modelNames = "VVE")
model_selection_7_final <- Mclust(famd_dims_final_7,G=k,modelNames = "VVE")
model_selection_8_final <- Mclust(famd_dims_final_8,G=k,modelNames = "VVE")
model_selection_9_final <- Mclust(famd_dims_final_9,G=k, modelNames = "VVE")

model_selection_11_final <- Mclust(famd_dims_final_11,G=k,modelNames = "VVE")
model_selection_12_final <- Mclust(famd_dims_final_12,G=k,modelNames = "VVE")
model_selection_13_final <- Mclust(famd_dims_final_13,G=k,modelNames = "VVE")
model_selection_14_final <- Mclust(famd_dims_final_14,G=k,modelNames = "VVE")
model_selection_15_final <- Mclust(famd_dims_final_15,G=k,modelNames = "VVE")
model_selection_16_final <- Mclust(famd_dims_final_16,G=k, modelNames = "VVE")

model_selection_17_final <- Mclust(famd_dims_final_17,G=k,modelNames = "VVE")
model_selection_18_final <- Mclust(famd_dims_final_18,G=k,modelNames = "VVE")
model_selection_19_final <- Mclust(famd_dims_final_19,G=k,modelNames = "VVE")
model_selection_21_final <- Mclust(famd_dims_final_21,G=k,modelNames = "VVE")
model_selection_22_final <- Mclust(famd_dims_final_22,G=k,modelNames = "VVE")
model_selection_23_final <- Mclust(famd_dims_final_23,G=k, modelNames = "VVE")

model_selection_24_final <- Mclust(famd_dims_final_24,G=k,modelNames = "VVE")


# Get the assigned cluster for each row in your data
client_clusters <- model_selection_final$classification
client_clusters_2 <- model_selection_2_final$classification
client_clusters_5 <- model_selection_5_final$classification
client_clusters_10 <- model_selection_10_final$classification
client_clusters_20 <- model_selection_20_final$classification
client_clusters_25 <- model_selection_25_final$classification

client_clusters_3 <- model_selection_3_final$classification
client_clusters_4 <- model_selection_4_final$classification
client_clusters_6 <- model_selection_6_final$classification
client_clusters_7 <- model_selection_7_final$classification
client_clusters_8 <- model_selection_8_final$classification
client_clusters_9 <- model_selection_9_final$classification

client_clusters_11 <- model_selection_11_final$classification
client_clusters_12 <- model_selection_12_final$classification
client_clusters_13 <- model_selection_13_final$classification
client_clusters_14 <- model_selection_14_final$classification
client_clusters_15 <- model_selection_15_final$classification
client_clusters_16 <- model_selection_16_final$classification

client_clusters_17 <- model_selection_17_final$classification
client_clusters_18 <- model_selection_18_final$classification
client_clusters_19 <- model_selection_19_final$classification
client_clusters_21 <- model_selection_21_final$classification
client_clusters_22 <- model_selection_22_final$classification
client_clusters_23 <- model_selection_23_final$classification

client_clusters_24 <- model_selection_24_final$classification


# shows in which cluster each observation belongs + the prob
# ie this just creates a new dataset with all info we need for every row for every dataset
df_final <- cbind(X_1_reduced, Cluster = client_clusters)
df_final_2 <- cbind(X_2_reduced, Cluster = client_clusters_2)
df_final_5 <- cbind(X_5_reduced, Cluster = client_clusters_5)
df_final_10 <- cbind(X_10_reduced, Cluster = client_clusters_10)
df_final_20 <- cbind(X_20_reduced, Cluster = client_clusters_20)
df_final_25 <- cbind(X_25_reduced, Cluster = client_clusters_25)

df_final_3 <- cbind(X_3_reduced, Cluster = client_clusters_3)
df_final_4 <- cbind(X_4_reduced, Cluster = client_clusters_4)
df_final_6 <- cbind(X_6_reduced, Cluster = client_clusters_6)
df_final_7 <- cbind(X_7_reduced, Cluster = client_clusters_7)
df_final_8 <- cbind(X_8_reduced, Cluster = client_clusters_8)
df_final_9 <- cbind(X_9_reduced, Cluster = client_clusters_9)

df_final_11 <- cbind(X_11_reduced, Cluster = client_clusters_11)
df_final_12 <- cbind(X_12_reduced, Cluster = client_clusters_12)
df_final_13 <- cbind(X_13_reduced, Cluster = client_clusters_13)
df_final_14 <- cbind(X_14_reduced, Cluster = client_clusters_14)
df_final_15 <- cbind(X_15_reduced, Cluster = client_clusters_15)
df_final_16 <- cbind(X_16_reduced, Cluster = client_clusters_16)

df_final_17 <- cbind(X_17_reduced, Cluster = client_clusters_17)
df_final_18 <- cbind(X_18_reduced, Cluster = client_clusters_18)
df_final_19 <- cbind(X_19_reduced, Cluster = client_clusters_19)
df_final_21 <- cbind(X_21_reduced, Cluster = client_clusters_21)
df_final_22 <- cbind(X_22_reduced, Cluster = client_clusters_22)
df_final_23 <- cbind(X_23_reduced, Cluster = client_clusters_23)

df_final_24 <- cbind(X_24_reduced, Cluster = client_clusters_24)


#  this is each row of each datasets probability of belonging to each cluster
probs <- model_selection_final$z 
probs_5 <- model_selection_5_final$z 
probs_25 <- model_selection_25_final$z 

probs_2 <- model_selection_2_final$z 
probs_3 <- model_selection_3_final$z 
probs_4 <- model_selection_4_final$z 

probs_6 <- model_selection_6_final$z 
probs_7 <- model_selection_7_final$z 
probs_8 <- model_selection_8_final$z 

probs_9 <- model_selection_9_final$z 
probs_10 <- model_selection_10_final$z 
probs_11 <- model_selection_11_final$z 

probs_12 <- model_selection_12_final$z 
probs_13 <- model_selection_13_final$z 
probs_14 <- model_selection_14_final$z 

probs_15 <- model_selection_15_final$z 
probs_16 <- model_selection_16_final$z 
probs_17 <- model_selection_17_final$z 

probs_18 <- model_selection_18_final$z 
probs_19 <- model_selection_19_final$z 
probs_20 <- model_selection_20_final$z 

probs_21 <- model_selection_21_final$z 
probs_22 <- model_selection_22_final$z 
probs_23 <- model_selection_23_final$z 

probs_24 <- model_selection_24_final$z

```

# Just saves the things so dont have to run entire thing again
```{r}
# 1. Group them into a single list object
all_models_list <- list(
  m1  = model_selection_final,    m2  = model_selection_2_final,  m3  = model_selection_3_final,
  m4  = model_selection_4_final,  m5  = model_selection_5_final,  m6  = model_selection_6_final,
  m7  = model_selection_7_final,  m8  = model_selection_8_final,  m9  = model_selection_9_final,
  m10 = model_selection_10_final, m11 = model_selection_11_final, m12 = model_selection_12_final,
  m13 = model_selection_13_final, m14 = model_selection_14_final, m15 = model_selection_15_final,
  m16 = model_selection_16_final, m17 = model_selection_17_final, m18 = model_selection_18_final,
  m19 = model_selection_19_final, m20 = model_selection_20_final, m21 = model_selection_21_final,
  m22 = model_selection_22_final, m23 = model_selection_23_final, m24 = model_selection_24_final,
  m25 = model_selection_25_final
)

# 2. Save the list to your hard drive
saveRDS(all_models_list, "mclust_final_models.rds")

```
# run this to get the mclust data stuff

```{r}

# Load the RDS file (make sure the file is in your working directory)
all_models_list <- readRDS("mclust_final_models.rds")

# extract them to be able to run the next chunks 
model_selection_final    <- all_models_list$m1
model_selection_2_final  <- all_models_list$m2
model_selection_3_final  <- all_models_list$m3
model_selection_4_final  <- all_models_list$m4
model_selection_5_final  <- all_models_list$m5
model_selection_6_final  <- all_models_list$m6
model_selection_7_final  <- all_models_list$m7
model_selection_8_final  <- all_models_list$m8
model_selection_9_final  <- all_models_list$m9
model_selection_10_final <- all_models_list$m10
model_selection_11_final <- all_models_list$m11
model_selection_12_final <- all_models_list$m12
model_selection_13_final <- all_models_list$m13
model_selection_14_final <- all_models_list$m14
model_selection_15_final <- all_models_list$m15
model_selection_16_final <- all_models_list$m16
model_selection_17_final <- all_models_list$m17
model_selection_18_final <- all_models_list$m18
model_selection_19_final <- all_models_list$m19
model_selection_20_final <- all_models_list$m20
model_selection_21_final <- all_models_list$m21
model_selection_22_final <- all_models_list$m22
model_selection_23_final <- all_models_list$m23
model_selection_24_final <- all_models_list$m24
model_selection_25_final <- all_models_list$m25

# now continue with the next chunks directly from here

```


 ###### label matching. #######
# to ensure every row across datsets are matched 
# since cluster 1 in dataset 1 does not necessarily mean the same as cluster 1 in dataste 20

# this code checks how similar each cluster accross each dataset is
# so that we can firstly see what clusters are actually the same accross different dataset (like c1 in d1 can be the same as c3 in d10)
# it does this compared to dataset 1 (can be any) as the reference dataset 
# so every cluster in dataset 2-25 is renamed to match clusters in dataset 1


# it checks how similar each cluster over each dataset is
# clusters with similar observations should be the same cluster 
# since similar obs should be in similar clusters
# if clusters tend to have the same type of observations in it just renames it in datasets 2-25 to match that of reference dataset
# (whole thing is called Hungarian algorithm)
# we then use Rubins Rule to poole the results based on the probabilities
# this is in that pdf file about the missingness i sent 

```{r}
library(clue)  # for Hungarian algorithm (solve_LSAP)

# Collect all classification vectors into a list
all_models <- list(
  model_selection_final,    model_selection_2_final,  model_selection_3_final,
  model_selection_4_final,  model_selection_5_final,  model_selection_6_final,
  model_selection_7_final,  model_selection_8_final,  model_selection_9_final,
  model_selection_10_final, model_selection_11_final, model_selection_12_final,
  model_selection_13_final, model_selection_14_final, model_selection_15_final,
  model_selection_16_final, model_selection_17_final, model_selection_18_final,
  model_selection_19_final, model_selection_20_final, model_selection_21_final,
  model_selection_22_final, model_selection_23_final, model_selection_24_final,
  model_selection_25_final
)

# Extract posterior probability matrices (n x G)
all_probs <- lapply(all_models, function(m) m$z)  # m$z is the n x 4 posterior matrix

# Align labels of each dataset to Dataset 1 (reference) using Hungarian algorithm
# For each imputation, find the permutation of clusters that best matches
# the reference posterior matrix, then reorder columns accordingly.
reference_probs <- all_probs[[1]]  # Dataset 1 is the reference

align_labels <- function(ref_probs, target_probs) {
  G <- ncol(ref_probs)
  
  # Build a cost matrix: how dissimilar is ref cluster g to target cluster k
  # Use sum of squared differences in posterior probabilities
  cost_matrix <- matrix(0, G, G)
  for (g in 1:G) {
    for (k in 1:G) {
      cost_matrix[g, k] <- sum((ref_probs[, g] - target_probs[, k])^2)
    }
  }
  
  # Hungarian algorithm finds the best column permutation
  # solve_LSAP(cost_matrix)[g] = which target column best matches ref column g
  perm <- as.integer(solve_LSAP(cost_matrix))
  
  # CRITICAL FIX: invert the permutation so that column g of the result
  # correctly corresponds to ref cluster g (not the raw perm which goes the other direction)
  inv_perm <- order(perm)
  
  # Return reordered posterior matrix
  return(target_probs[, inv_perm])
}

aligned_probs <- vector("list", length(all_probs))
aligned_probs[[1]] <- reference_probs  # reference stays same here

for (i in 2:length(all_probs)) {
  aligned_probs[[i]] <- align_labels(reference_probs, all_probs[[i]])
  
  # Diagnostic: check correlation between aligned dataset and reference per cluster
  # all 4 values should be high — if any drop near zero, that dataset's alignment failed
  corr <- diag(cor(reference_probs, aligned_probs[[i]]))
  cat("Dataset", i, "- per-cluster correlation with reference:", round(corr, 3), "\n")
}

# hier is Rubin's Rule: average the aligned posterior probabilities
# Die is the "across imputation" pooling step
pooled_probs <- Reduce("+", aligned_probs) / length(aligned_probs)

# Sanity check: all 4 cluster columns should have non-trivial means
# if any column is near 0 across the board, alignment collapsed that cluster
cat("\nPooled prob column means (should all be non-trivial):\n")
print(colMeans(pooled_probs))

# Assign final cluster = highest pooled posterior probability
final_clusters <- apply(pooled_probs, 1, which.max)


# X_1$final_cluster <- as.factor(final_clusters)
# data with missing values and clusters
# just to show with the missing data that we still cluster into cluster x
# should not have a value here as there is not a real value to enter here
# we have a range/distribution of values that could possibly be the real values
All_data_to_show <- data_final
All_data_to_show$final_cluster    <- as.factor(final_clusters)
All_data_to_show$prob_in_cluster  <- pooled_probs[cbind(1:nrow(pooled_probs), final_clusters)]
All_data_to_show$prob_cluster_1   <- pooled_probs[, 1]
All_data_to_show$prob_cluster_2   <- pooled_probs[, 2]
All_data_to_show$prob_cluster_3   <- pooled_probs[, 3]
All_data_to_show$prob_cluster_4   <- pooled_probs[, 4]

```

# This helps decide how we differentiate between clusters
# my thinking is just that we know its bank data
# but we dont truly know what type of bank data it is for
# it is probably be credit risk so high/medium/low risk
# but
# it may be customer profitability
# attrition and churn prediction (if the customer will leave the bank)
# model the type of customer (is it like an up and coming business, old person looking to retire, young person that might want a house loan)
# so i was thinking we rather cluster based on attributes of the data than an outcome we think they might be looking for
# Since we dont with 100% certainty know what we are truly clustering
# Atleast that is my thinking
# go through this and check if you agree.
```{r}

# Create analysis dataframe with pooled clusters
analysis_df <- X_1_reduced  # Use one version of the data
analysis_df$final_cluster <- All_data_to_show$final_cluster
analysis_df$cluster_prob <- All_data_to_show$prob_in_cluster

# Calculate cluster means for numeric variables
numeric_vars <- names(analysis_df)[sapply(analysis_df, is.numeric) & 
                                     names(analysis_df) != "final_cluster" &
                                     names(analysis_df) != "cluster_prob"]

cluster_means_pooled <- aggregate(analysis_df[, numeric_vars], 
                                  by = list(Cluster = analysis_df$final_cluster), 
                                  FUN = mean, na.rm = TRUE)

print("=== POOLED CLUSTER MEANS (After Multiple Imputation) ===")


# For categorical variables
categorical_vars <- names(analysis_df)[!sapply(analysis_df, is.numeric) & 
                                         names(analysis_df) != "final_cluster"]

for(var in categorical_vars) {
  cat("\n=== CATEGORICAL VARIABLE:", var, "===\n")
  print(table(analysis_df$final_cluster, analysis_df[[var]]))
  print(round(prop.table(table(analysis_df$final_cluster, analysis_df[[var]]), margin = 1), 3))
}

# Weighted cluster profiles (accounts for uncertainty in assignments)
library(dplyr)

weighted_profiles <- analysis_df %>%
  group_by(final_cluster) %>%
  summarise(
    # Weighted means using cluster probability
    Annual_Revenue = weighted.mean(annual_revenue_m, cluster_prob, na.rm = TRUE),
    Cash_Share = weighted.mean(cash_share, cluster_prob, na.rm = TRUE),
    Supplier_Conc = weighted.mean(supplier_concentration, cluster_prob, na.rm = TRUE),
    Customer_Conc = weighted.mean(customer_concentration, cluster_prob, na.rm = TRUE),
    Engagement = weighted.mean(client_engagement_score, cluster_prob, na.rm = TRUE),
    # Unweighted for comparison
    N = n(),
    Avg_Probability = mean(cluster_prob, na.rm = TRUE)
  )

print(weighted_profiles)

# Discriminant analysis on pooled clusters
library(MASS)

# Use only high-confidence assignments (optional - probability > 0.7)
high_confidence <- analysis_df[analysis_df$cluster_prob > 0.7, ]

lda_pooled <- lda(final_cluster ~ ., 
                  data = high_confidence[, c(numeric_vars, "final_cluster")])

print("=== VARIABLE IMPORTANCE (Pooled Data) ===")
print(round(lda_pooled$scaling, 3))

# Heatmap of pooled cluster profiles
library(pheatmap)

# Standardize numeric variables
scaled_pooled <- scale(cluster_means_pooled[, -1])
rownames(scaled_pooled) <- paste("Cluster", cluster_means_pooled$Cluster)

pheatmap(scaled_pooled,
         main = "POOLED CLUSTER PROFILES (After Multiple Imputation)",
         color = colorRampPalette(c("blue", "white", "red"))(50),
         display_numbers = TRUE)

# Check how confident the assignments are
confidence_summary <- analysis_df %>%
  group_by(final_cluster) %>%
  summarise(
    Count = n(),
    Mean_Probability = mean(cluster_prob),
    Min_Prob = min(cluster_prob),
    Max_Prob = max(cluster_prob),
    Pct_HighConfidence = sum(cluster_prob > 0.7) / n() * 100
  )

print(confidence_summary)

# Histogram of cluster probabilities
# ggplot(analysis_df, aes(x = cluster_prob, fill = factor(final_cluster))) +
#   geom_histogram(bins = 30, alpha = 0.7) +
#   facet_wrap(~final_cluster) +
#   labs(title = "Cluster Assignment Confidence by Final Cluster",
#        x = "Probability of Assignment", y = "Count") +
#   theme_minimal()

# Create definitive names based on your actual outputs
# Definitive names using only sector, cash share, and revenue
final_cluster_names <- c(
  "1" = "Diverse Portfolio (High Revenue, Medium Cash)",
  "2" = "Agriculture-Led Mixed (Medium Revenue, Low Cash)", 
  "3" = "Healthcare Pure Play (Low Revenue, Low Cash)",
  "4" = "Construction (Low Revenue, Low Cash)"
)

# Even more descriptive (with estimates - update once you have actual numbers)
detailed_names <- c(
  "1" = "Diverse Portfolio (~High Revenue, ~21% Cash)",
  "2" = "Agriculture-Led Mixed (~Medium Revenue, ~20% Cash)", 
  "3" = "Healthcare Pure Play (~Low Revenue, ~20% Cash)",
  "4" = "Construction (~Low Revenue, ~20% Cash)"
)

# Shorter version for reports
short_names <- c(
  "1" = "Diverse: High Rev, Med Cash",
  "2" = "Agriculture Mix: Med Rev, Low Cash", 
  "3" = "Healthcare: Low Rev, Low Cash",
  "4" = "Construction: Low Rev, Low Cash"
)
```
# ============================================================
# HEATMAP USING ACTUAL CLUSTER MEANS
# + TOP DRIVERS FROM POOLED FAMD CONTRIBUTIONS
# ============================================================

library(dplyr)
library(tidyr)
library(ggplot2)

# ------------------------------------------------------------
# 1. BUILD POOLED FAMD CONTRIBUTIONS
# ------------------------------------------------------------

# Use ALL FAMD contribution results
all_total_contribs <- list(
  total_contribs,
  total_contribs_2,
  total_contribs_3,
  total_contribs_4,
  total_contribs_5,
  total_contribs_6,
  total_contribs_7,
  total_contribs_8,
  total_contribs_9,
  total_contribs_10,
  total_contribs_11,
  total_contribs_12,
  total_contribs_13,
  total_contribs_14,
  total_contribs_15,
  total_contribs_16,
  total_contribs_17,
  total_contribs_18,
  total_contribs_19,
  total_contribs_20,
  total_contribs_21,
  total_contribs_22,
  total_contribs_23,
  total_contribs_24,
  total_contribs_25
)

# Convert to matrix
contrib_matrix <- do.call(
  cbind,
  lapply(all_total_contribs, function(x) {
    x[order(names(x))]
  })
)

rownames(contrib_matrix) <- sort(names(total_contribs))

# Pooled contribution across imputations
pooled_total_contribs <- rowMeans(contrib_matrix)

# ------------------------------------------------------------
# 2. CREATE STACKED DATASET
# ------------------------------------------------------------

stacked_data <- analysis_df

# ------------------------------------------------------------
# 3. TOP VARIABLES FROM POOLED FAMD CONTRIBUTIONS
# ------------------------------------------------------------

driver_table <- data.frame(
  Variable = names(pooled_total_contribs),
  Contribution = pooled_total_contribs
) %>%
  arrange(desc(Contribution))

# Keep only numeric variables
top_numeric_vars <- driver_table$Variable[
  driver_table$Variable %in% numeric_vars
]

# Choose top N variables
top_n <- 15

top_numeric_vars <- top_numeric_vars[
  1:min(top_n, length(top_numeric_vars))
]

cat("\n=================================================\n")
cat("TOP VARIABLES USED IN HEATMAP\n")
cat("=================================================\n")

print(top_numeric_vars)

# ------------------------------------------------------------
# 4. COMPUTE ACTUAL CLUSTER MEANS
# ------------------------------------------------------------

cluster_means_actual <- stacked_data %>%
  group_by(final_cluster) %>%
  summarise(
    across(
      all_of(top_numeric_vars),
      ~mean(.x, na.rm = TRUE)
    ),
    .groups = "drop"
  )

print(cluster_means_actual)

# ------------------------------------------------------------
# 5. CONVERT TO LONG FORMAT
# ------------------------------------------------------------

cluster_means_long <- cluster_means_actual %>%
  pivot_longer(
    cols = -final_cluster,
    names_to = "Variable",
    values_to = "Mean_Value"
  )

# ------------------------------------------------------------
# 6. ROUND LABELS
# ------------------------------------------------------------

cluster_means_long <- cluster_means_long %>%
  mutate(
    Label = round(Mean_Value, 2)
  )

# ------------------------------------------------------------
# 7. HEATMAP OF ACTUAL MEANS
# ------------------------------------------------------------

ggplot(
  cluster_means_long,
  aes(
    x = Variable,
    y = paste("Cluster", final_cluster),
    fill = Mean_Value
  )
) +

  geom_tile(color = "white") +

  geom_text(
    aes(label = Label),
    size = 3
  ) +

  scale_fill_gradient2(
    low = "blue",
    mid = "white",
    high = "red",
    midpoint = median(
      cluster_means_long$Mean_Value,
      na.rm = TRUE
    )
  ) +

  labs(
    title = "Cluster Profiles Using Actual Means",
    subtitle = "Top numeric drivers from pooled FAMD contributions",
    x = "Variables",
    y = ""
  ) +

  theme_minimal(base_size = 12) +

  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    ),
    panel.grid = element_blank()
  )


cluster_means_table <- cluster_means_actual %>%
  mutate(across(where(is.numeric), ~round(.x, 2)))

print(cluster_means_table)


# ------------------------------------------------------------
# 8. OPTIONAL: STANDARDISED VERSION
# ------------------------------------------------------------

cluster_means_scaled <- cluster_means_actual

cluster_means_scaled[, -1] <- scale(
  cluster_means_scaled[, -1]
)

cluster_means_scaled_long <- cluster_means_scaled %>%
  pivot_longer(
    cols = -final_cluster,
    names_to = "Variable",
    values_to = "Scaled_Value"
  ) %>%
  mutate(
    Label = round(Scaled_Value, 2)
  )

ggplot(
  cluster_means_scaled_long,
  aes(
    x = Variable,
    y = paste("Cluster", final_cluster),
    fill = Scaled_Value
  )
) +

  geom_tile(color = "white") +

  geom_text(
    aes(label = Label),
    size = 3
  ) +

  scale_fill_gradient2(
    low = "blue",
    mid = "white",
    high = "red",
    midpoint = 0
  ) +

  labs(
    title = "Standardised Cluster Heatmap",
    subtitle = "Values shown as deviations from overall mean",
    x = "Variables",
    y = ""
  ) +

  theme_minimal(base_size = 12) +

  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    ),
    panel.grid = element_blank()
  )

# ------------------------------------------------------------
# 9. SAVE TABLE
# ------------------------------------------------------------

write.csv(
  cluster_means_actual,
  "cluster_means_actual.csv",
  row.names = FALSE
)

# ------------------------------------------------------------
# 10. CLUSTER-SPECIFIC INTERPRETATION TABLES
# ------------------------------------------------------------

for(k in unique(cluster_means_actual$final_cluster)) {

  cat("\n=================================================\n")
  cat("CLUSTER", k, "\n")
  cat("=================================================\n")

  tmp <- cluster_means_long %>%
    filter(final_cluster == k) %>%
    arrange(desc(Mean_Value))

  print(tmp)
}

# ------------------------------------------------------------
# 11. OPTIONAL: RELATIVE DIFFERENCE VS OVERALL MEAN
# ------------------------------------------------------------

overall_means <- stacked_data %>%
  summarise(
    across(
      all_of(top_numeric_vars),
      ~mean(.x, na.rm = TRUE)
    )
  )

relative_profiles <- cluster_means_actual

for(v in top_numeric_vars){

  relative_profiles[[v]] <-
    (
      cluster_means_actual[[v]] -
      overall_means[[v]]
    ) / overall_means[[v]] * 100
}

relative_long <- relative_profiles %>%
  pivot_longer(
    cols = -final_cluster,
    names_to = "Variable",
    values_to = "Pct_Diff"
  ) %>%
  mutate(
    Label = paste0(round(Pct_Diff,1), "%")
  )

ggplot(
  relative_long,
  aes(
    x = Variable,
    y = paste("Cluster", final_cluster),
    fill = Pct_Diff
  )
) +

  geom_tile(color = "white") +

  geom_text(
    aes(label = Label),
    size = 3
  ) +

  scale_fill_gradient2(
    low = "blue",
    mid = "white",
    high = "red",
    midpoint = 0
  ) +

  labs(
    title = "Relative Cluster Profiles vs Overall Portfolio",
    subtitle = "% above/below portfolio average",
    x = "Variables",
    y = ""
  ) +

  theme_minimal(base_size = 12) +

  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    ),
    panel.grid = element_blank()
  )